Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-21 paper.tex
Progress :)

\subsubsectionx{Malicious adversary}

@@

An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set. Here, \(n\) is the number of total parties, and \(t\) is number of possible adversaries while not revealing any secrets.\\

@@

\subsection{SPDZ 2.0 in medical healthcare}
In medical healthcare, preserving privacy plays a huge role because patient records hold highly sensitive data, thus, its a natural area for the application of privacy protecting technologies. In [TODO: REFERENCE] a clinical decision support system was implemented with SPDZ 2.0. The idea is that the system provides the optimal treatment for a patient with HIV based on the  records of similar patients in different hospitals. To preserve privacy, the hospitals compute the efficiency of one treatment for one patient together with SMPC.\\
The researchers used a setup of 20.000 patient records split between the hospitals, and were able to compute the effectiveness of 100 treatments for one patient in 24 minutes in the online phase. For calculating the effectiveness of one treatment, their algorithm needed 40 million multiplications. They only implemented the online phase of SPDZ, but showed that it scaled linearly with the amount of patient records. In the paper the amount of parties participating in the computation was not specified, but because the computation is quite good, it can be assumed that a really simple setup is used that doesn't create a lot of overhead.

@@

https://www.researchgate.net/publication/328040632A\_New\_Approach\_to\_Privacy-Preserving\_Clinical\_Decision\_Support\_Systems\_for\_HIV\_Treatment
https://arxiv.org/pdf/1901.00329.pdf
https://www.researchgate.net/publication/324077995\_SEMBASEcure\_multi-biometric\_authentication

@@

>>>>

\subsubsection{Malicious adversary}

@@

An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set. Here, \(n\) is the number of total parties, and \(t\) is number of possible adversaries while not revealing any secrets ~\cite{MPCBook_threshold}.\\

@@

\subsection{SPDZ 2.0 in medical healthcare}
In medical healthcare, preserving privacy plays a huge role because patient records hold highly sensitive data, thus, its a natural area for the application of privacy protecting technologies. In ~\cite{PPCDSS} a clinical decision support system was implemented with SPDZ 2.0. The idea is that the system provides the optimal treatment for a patient with HIV based on the  records of similar patients in different hospitals. To preserve privacy, the hospitals compute the efficiency of one treatment for one patient together with SMPC.\\
The researchers used a setup of 20.000 patient records split between the hospitals, and were able to compute the effectiveness of 100 treatments for one patient in 24 minutes in the online phase. For calculating the effectiveness of one treatment, their algorithm needed 40 million multiplications. They only implemented the online phase of SPDZ, but showed that it scaled linearly with the amount of patient records. In the paper the amount of parties participating in the computation was not specified, but because the computation is quite good, it can be assumed that a really simple setup is used that doesn't create a lot of overhead.

@@

\subsection{Other implementations}

In ~\cite{SEMBA} an implementation of biometric-based authentication, i.e. iris and face authentication, with SPDZ was shown. The researchers were able to improve existing solutions with the use of SPDZ.\\

~\cite{2019arXiv190100329C} implemented typical machine learning algorithms like linear and logistic regression with SPDZ and showed that it outperforms a competing protocols Obliv-C ~\cite{cryptoeprint:2015:1153} and matches SecureML ~\cite{SecureML}. So it can be assumed, that an implementation with SCALE-MAMBA would show even better results.\\

@@

While SPDZ might be the best multi party protocol, in X it was compared to tw

Two party protocols
~\cite{MPCCompression}
In X it was shown, that SPDZ 2.- has vulnerabilities. It was compared to the three most cited two party protocols, and it was shown that for a specific attack, SPDZ is the most vulnerable of these. It was as well shown, that the secret sharing is predictable. The researchers didnt analyze, if this is still the case in SCALE-MAMBA.
TinyLego ~\cite{TinyLego}
Duplo ~\cite{Duplo}
~\cite{Aby}

Nevertheless, in a two party settings there are more secure protocols.
